---
title: "Introduction to Dose-Response Physical Activity (drpa) package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{drpa}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>", root.dir = 'vignettes')
options(tibble.print_min = 4L, tibble.print_max = 4L, rmarkdown.html_vignette.check_title = FALSE)
```

## Installation from GitHub

The package is not available at CRAN. It needs to be installed from GitHub. Please use this command to install it.

```{r install, eval=FALSE}
remotes::install_github("meta-analyses/drpa")
```

You may need to install the `remotes` package first.

## List of diseases/cause and their upper limit

The first column `disease` specifies the supported diseases in the package. The other three columns, which are outcome types (`fatal`, `non-fatal` and `fatal-and-non-fatal`), show the last knot (based on the available data points) for the specific disease. We don't have confidence that our meta-analysis is reliable after this point, and assumes an onward flat relationship. Whenever a disease such as `all-cause-cvd` doesn't have an outcome type `non-fatal`, it will be `NA`. More will follow in the next section.

```{r echo=FALSE, message=FALSE}

require(kableExtra)

dtable <- readr::read_csv('../inst/extdata/75p_diseases.csv')

kbl(dtable) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Setup

Load the package

```{r setup}
library(drpa)
```

## Get dose response relationship

Get response for dose *4*0 for *all-cause-cvd*

```{r}

drpa::dose_response(cause = 'all-cause-cvd', outcome_type = "fatal-and-non-fatal", 
                    dose = 40, confidence_intervals = TRUE, certainty = TRUE)


```

### Arguments

Description of the arguments are mentioned below:

+----------------------+-------------------------------------------------------------------------------------------------------+
| Argument             | Description                                                                                           |
+======================+=======================================================================================================+
| cause                | All-cause-mortality or disease name                                                                   |
+----------------------+-------------------------------------------------------------------------------------------------------+
| outcome_type         | Either one of the three possibilities for outcome type: fatal, non-fatal or fatal-and-non-fatal                                                               |
+----------------------+-------------------------------------------------------------------------------------------------------+
| dose                 | Dose (all-cause or disease)                                                                           |
+----------------------+-------------------------------------------------------------------------------------------------------+
| confidence_intervals | Boolean variable to determine whether confidence intervals are returned or not - default false        |
+----------------------+-------------------------------------------------------------------------------------------------------+
| certainty            | Certain response (fixed) or uncertain in the range of lower and upper bounds - default is certain (T) |
+----------------------+-------------------------------------------------------------------------------------------------------+
| use_75_pert          | Last quantile determined by person years; beyond which there is less confidence                       |
+----------------------+-------------------------------------------------------------------------------------------------------+
