---
title: "Introduction to Dose-Response Physical Activity (drpa) package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{drpa}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>", root.dir = 'vignettes')
options(tibble.print_min = 4L, tibble.print_max = 4L, rmarkdown.html_vignette.check_title = FALSE)
```

Last updated on: `r format(Sys.Date(), '%d %B, %Y')`

## Installation from GitHub

The package is not available at CRAN. It needs to be installed from GitHub. Please use this command to install it.

```{r install, eval=FALSE}
remotes::install_github("meta-analyses/drpa")
```

You may need to install the `remotes` package first.

## List of diseases/cause and their upper limit

The first column `disease` specifies the supported diseases in the package. The other three columns, which are outcome types (`fatal`, `non-fatal` and `fatal-and-non-fatal`), show the last knot (based on the available data points) for the specific disease. We don't have confidence that our meta-analysis is reliable after this point, and assumes an onward flat relationship. Whenever a disease such as `all-cause-cvd` doesn't have an outcome type `non-fatal`, it will be `NA`. More will follow in the next section.

```{r echo=FALSE, message=FALSE}
library(magrittr)
require(kableExtra)

dtable <- readr::read_csv('../inst/extdata/75p_diseases.csv')

kbl(dtable) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Setup

Load the package

```{r setup}
library(drpa)
```

## Get dose response relationship

Get response for dose *40* for *all-cause-cvd* with the default quantile *0.5* and censoring at doubling of WHO's recommended level of physical activity for adults (*17.5* MMETs hours per week).

The `quantile`'s value is between 0 and 1 [excluding the boundary values]

```{r}

drpa::dose_response(cause = 'all-cause-cvd', outcome_type = 'fatal-and-non-fatal', dose = 40, 
                    quantile = 0.5, confidence_intervals = T, censor_method = 'WHO-DRL')


```

### Arguments

Description of the arguments are mentioned below:

| Argument             | Description                                                                                                                                                                                                                                                                                                                                                                                                          |
|-----------------|-------------------------------------------------------|
| cause                | All-cause-mortality or disease name                                                                                                                                                                                                                                                                                                                                                                                  |
| outcome_type         | Either one of the three possibilities for outcome type: fatal, non-fatal or fatal-and-non-fatal                                                                                                                                                                                                                                                                                                                      |
| dose                 | Dose (all-cause or disease)                                                                                                                                                                                                                                                                                                                                                                                          |
| quantile             | Numeric value between 0 and 1 - default is `0.5`. This captures the range of dose values between `lower` and `upper` confidence levels.                                                                                                                                                                                                                                                                              |
| censor_method        | This determines whether any censor method applies to the dose-response relationship. There are four possibilities: `none`, `75thPercentile`(to use 75th percentile using person years), `WHO-DRL` (WHO's recommended physical activity per week `8.75` when doubled, so `17.5` MMETs hours per week) or `WHO-QRL` (WHO's recommended physical activity per week `8.75` when quadrupled, so `35` MMETs hours per week) . The default value is `WHO-DRL` - a fixed censor point at `17.5` after which the relationship remains the same. |
| confidence_intervals | Boolean variable to determine whether confidence intervals are returned or not - default false                                                                                                                                                                                                                                                                                                                       |
